The Impact of Education <br>

### 2014-12-07 PresentationandPaper/Presentation/EdEntrePres.Rmd
Created missing README files, deleted unneccesary files, and cleaned repository.

- Since we look at average individual self-esteem in every OECD country, we believe it is appropriate to look at the opportunities perceived by the average 18-64-year-old individual in these countries.

>>>>

- Since we look at average individual self-confidence in every OECD country, we believe it is appropriate to look at the opportunities perceived by the average 18-64-year-old individual in these countries.
